---
title: "R Notebook"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
library(tidyverse)
library(palmerpenguins)

penguins_df <- penguins
penguins_df
```

# Running a Chi Squared Test for Independence

```{r}
chisq.test(x = penguins_df$species, y = penguins_df$sex)
```

H_null: Penguin species and sex are independent H_alternative: Penguins
species and sex are NOT independent

Conclusion: We fail to reject the null hypothesis and conclude that
penguins species and sex are independent

# One Way ANOVA

H_null: Means of all the groups are not different H_alternative: The
mean of at least one of the groups is different

## Descriptive Stats

Interested in the flipper size of penguins

```{r}
penguins_df %>%
  group_by(species) %>%
  summarize(
    mean_flipper_length = mean(flipper_length_mm, na.rm = TRUE)
  )
```

```{r}
penguins_df %>%
  ggplot() +
    geom_boxplot(aes(y = species, x = flipper_length_mm, fill = species))
```

```{r}
model <- aov(flipper_length_mm ~ species, data = penguins_df)
summary(model)
```

H_null: Means of flipper lengths of all penguin species are not
different H_alternative: The mean flipper length of at least one penguin
species is different

Conclusions: We reject the null hypothesis and conclude that the mean
flipper length of at least one penguin species is different

# Post Hoc Analysis

```{r}
gentoo_flippers <- penguins_df %>%
  filter(species == "Gentoo", sex == "male") %>%
  pull(flipper_length_mm)
adelie_flippers <- penguins_df %>%
  filter(species == "Adelie", sex == "male") %>%
  pull(flipper_length_mm)
chinstrap_flippers <- penguins_df %>%
  filter(species == "Chinstrap", sex == "male") %>%
  pull(flipper_length_mm)
```

```{r}
gentoo_flippers
```

## Gentoo vs Adelie

```{r}
t.test(x = gentoo_flippers, y = adelie_flippers)
```

## Adelie vs Chinstrap

```{r}
t.test(x = chinstrap_flippers, y = adelie_flippers)
```

## Chinstrap vs Gentoo

```{r}
t.test(x = chinstrap_flippers, y = gentoo_flippers)
```

At a significance level of 0.05, the probability of a type I error for
one is 0.05 For two tests, it would be 1 - (1 - 0.05)\^2 For 3 tests, it
would be 1 - (1- 0.05)\^3

```{r}
 1 - (1 - 0.05)^2
```

```{r}
 1 - (1 - 0.05)^3
```

Bonferroni Correction: Since we are doing 3 tests, we divide our
significance level by 3 Instead of comparing p_value. to significance
level for each test, compare p_value to significance_level/3 for each
test

```{r}
0.05/3
```

# Two way ANOVA

```{r}
model <- aov(flipper_length_mm ~ species * sex, data = penguins_df)
summary(model)
```

### 
